Extract team means and SDs

### 2022-09-12 scripts/r/07_team-sds.Rmd

```{r}
#| label: chelonia_brummeri
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 1532, 
  end = 1601
  )

@@

msa_mean_sd_df <- left_join(
  msa_mean_sd %>% 
    arrange(animal) %>% 
    mutate(row_n = row_number()), 
  assigned %>%
    filter(
      animal %in% teams, 
      exclude == "no", 
      outcome %in% c("duration", "intensity", "f0")
    ) %>% 
    select(animal, model_n, outcome, transformation) %>% 
    arrange(animal) %>% 
    mutate(row_n = row_number()), 
  by = c("animal", "row_n")
) %>% 
  mutate(model_n_match = if_else(model_n.x == model_n.y, 1, 0), 
    transformation = case_when(
      is.na(transformation) ~ 'none', 
      transformation == "NA" ~ 'none', 
      TRUE ~ transformation
    )) %>% 
  select(animal, model_n_rda = model_n.x, model_n_excel = model_n.y, model_n_match, 
         dv, outcome, transformation, mean, sd)

>>>>

```{r}
#| label: chelonia_brummeri
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 1532, 
  end = 1600
  )

@@

msa_mean_sd_df <- left_join(
  msa_mean_sd %>% 
    arrange(animal) %>% 
    mutate(row_n = row_number()), 
  assigned %>%
    filter(
      animal %in% teams, 
      exclude == "no", 
      outcome %in% c("duration", "intensity", "f0")
    ) %>% 
    select(animal, model_n, temporal_window, outcome, transformation) %>% 
    arrange(animal) %>% 
    mutate(row_n = row_number()), 
  by = c("animal", "row_n")
) %>% 
  mutate(model_n_match = if_else(model_n.x == model_n.y, 1, 0), 
    transformation = case_when(
      is.na(transformation) ~ 'none', 
      transformation == "NA" ~ 'none', 
      TRUE ~ transformation
    )) %>% 
  select(animal, model_n_rda = model_n.x, model_n_excel = model_n.y, model_n_match, 
         temporal_window, dv, outcome, transformation, mean, sd)
